Neural Connectome of the Ctenophore Statocyst

### 2025-05-06 manuscript/Manuscript.qmd
supplement figure

![**Figure 1—figure supplement 1**\
(A)...](figures/Supplemental_figure.png)

![**Figure 2—figure supplement 1**\
(A)...](figures/Supplemental_figure.png)

>>>>

![**Figure 1—figure supplement 1**\
(A)...](figures/Figure1_Supplement1.png)

![**Figure 2—figure supplement 1**\
(A)...](figures/Figure2_Supplement1.png)
